---
title: "Deliverable 1"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```



Start up code and loading R libraries: 

```{r}
#start up code 
#clear R
rm(list = ls())

#load the libraries 
library(scales)
library(ggplot2)
library(rio)
library(ggrepel)
```

Laading in the data from Git Hub: 

```{r}
#load the data from github 
link="https://github.com/Many-Plots-Here/deliv1/raw/main/Best_Movie_by_Year_Netflix.csv"

MovieFile=import(link)
View(MovieFile)
```

Create an absolute values table: 
```{r}
absoluteT=table(MovieFile$MAIN_GENRE,
                exclude = 'nothing')

absoluteT
```

Turn aboslute values table into a prop table and then convert entries into percents:
```{r}
prop.table(absoluteT) #create prop table 

GenrePercent=prop.table(absoluteT)*100 #turn them into percents 
GenrePercent

```

Convert the frequency table into a data frame 
```{r}
tableFreq=as.data.frame(absoluteT) #turn the frequency table into a data frame 

names(tableFreq)=c("Genre", "Count") #rename data frame columns 

tableFreq$Percent=as.vector(GenrePercent) #add column for percentages 

tableFreq #view the table 
```
Data visualization prep: 
```{r}
#create the base 
base=ggplot(data = tableFreq,
            aes(x = Genre, 
                y = Percent))
```

Plot 1: input the data 
```{r}
#add layer that produces the main plot 
plot1 = base + geom_bar(fill="Lightblue",
                        stat = 'identity')
plot1
```

Plot 2: Add titles 
```{r}
#adding titles
titleText='Best Movies on Netflix in 2022'
sourceText= 'Source: Kaggle.com Netflix TV Shows and Movies (2022)'

#add layer that adds the titles
plot2 = plot1 + labs(title=titleText,
                     x = NULL,
                     y = NULL,
                     caption = sourceText
                     )
plot2
```

Plot 3: Customize the vertical axes 
```{r}
#customize the vertical axes 
plot3 = plot2 + scale_y_continuous(breaks =  c(0, 5, 10, 20, 40),
                          limits = c(0, 45),
                          labels=unit_format(suffix = '%'))
plot3
```
Plot 4: Reposition the title and subtitle
```{r}
#reposition the title and subtitle
plot4 = plot3 + theme(plot.caption = element_text(hjust = 0), 
                      plot.title = element_text(hjust = 0.5))
plot4
```
Plot 5: Add value labels 
```{r}
#add values 
paste0(round(tableFreq$Percent,2), '%')
LABELS=paste0(round(tableFreq$Percent,2), '%')
###
plot5 = plot4 + geom_text(vjust=0, #hjust if flipping
                          size = 3,
                          aes(y = Percent ,
                              label = LABELS))
plot5

```
Ruruning the plots to have reordered bars:
```{r}
#ordering bars
tableFreq=tableFreq[order(tableFreq$Percent),]

(GenreOrd=tableFreq[order(tableFreq$Percent),'Genre'])

##adding this to the base 
LABELS=paste0(round(tableFreq$Percent,2), '%')
base= ggplot(data = tableFreq, 
             aes(x = Genre,y = Percent)) 
## adding these to base
base= base + scale_x_discrete(limits=GenreOrd) 
base= base + theme_classic()

#redo everything, copying from above 

#add layer that produces the main plot 
plot1 = base + geom_bar(fill = "Lightblue", color = "Black",
                        stat = 'identity')

#adding titles
titleText='Best Movies on Netflix in 2022'
sourceText= 'Source: Kaggle.com Netflix TV Shows and Movies (2022)'

#add layer that adds the titles
plot2 = plot1 + labs(title=titleText,
                     x = NULL,
                     y = NULL,
                     caption = sourceText
)


#customize the vertical axes 
plot3 = plot2 + scale_y_continuous(breaks =  c(0, 5, 10, 20, 40),
                                   limits = c(0, 45),
                                   labels=unit_format(suffix = '%'))

#reposition the title and subtitle
plot4 = plot3 + theme(plot.caption = element_text(hjust = 0), 
                      plot.title = element_text(hjust = 0.5))

#add values 
paste0(round(tableFreq$Percent,2), '%')
LABELS=paste0(round(tableFreq$Percent,2), '%')
###
plot5 = plot4 + geom_text(vjust=0, #hjust if flipping
                          size = 3,
                          aes(y = Percent ,
                              label = LABELS))
plot5
```
Adding text annotations:
```{r}
plot5 + annotate("text", x = 9, y = 30, 
                 label="There are more than 2.5x as 
                        many drama movies than comedy", size=2.5) + annotate("text", x=2.75, y = 11, 
           label="Action, documentary, fanstasy, war, 
           and western combined make up ~10% of movies", size=2.5)


```

